\documentclass[letterpaper,11pt]{article}

%packages
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[left=2cm,top=2cm,right=2cm,bottom=1.5cm,head=.5cm,foot=.5cm]{geometry}
\usepackage{url}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{subfig}
\usepackage{float}
\usepackage{setspace}
\usepackage{lineno}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{xr}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{hyperref}

%new commands and so on
\providecommand{\keywords}[1]
{
  \small	
  \textbf{\textit{Keywords---}} #1
}

\DeclareMathOperator{\E}{\mathbb{E}}% expected value
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\cov}{cov}
\DeclareMathOperator{\cor}{cor}
\DeclareMathOperator{\mean}{mean}
\DeclareMathOperator{\se}{se}
\DeclareMathOperator{\sd}{sd}
\DeclareMathOperator{\prob}{P}

%attempt 1 at nat and sharp
%\newcommand{\nat}{\mathlarger{\natural}}
%\newcommand{\shp}{\mathlarger{\sharp}}

%attempt 2 at nat and sharp
%\newcommand{\nat}{\raisebox{1pt}{\mathsmaller{\mathsmaller{/\hspace{-2pt}/}}}}
%\newcommand{\shp}{\#}

%attempt 3 at nat and sharp
\newcommand{\nat}{%
\text{\hspace{-1.5pt}
\begin{tikzpicture}[scale=1.8]%
\draw (.333ex,0) -- (.333ex,1ex);%
\draw (.666ex,0) -- (.666ex,1ex);
\end{tikzpicture}%
}}
\newcommand{\shp}{%
\text{\hspace{-1.5pt}
\begin{tikzpicture}[scale=1.8]%
\draw (0,.333ex) -- (1ex,.333ex);%
\draw (0,.666ex) -- (1ex,.666ex);%
\draw (.333ex,0) -- (.333ex,1ex);%
\draw (.666ex,0) -- (.666ex,1ex);
\end{tikzpicture}%
}}
\newcommand{\test}{%
\text{
\begin{tikzpicture}[scale=1.8]%
\draw (0,0) -- (1ex,0ex);
\draw (0,0) -- (0ex,1ex);
\draw (0,1ex) -- (1ex,1ex);
\draw (1ex,0) -- (1ex,1ex);
\draw (0,.333ex) -- (2ex,.333ex);%
\draw (0,.666ex) -- (1ex,.666ex);%
\draw (.333ex,0) -- (.333ex,1ex);%
\draw (.666ex,0) -- (.666ex,1ex);
\end{tikzpicture}%
}}

\newcommand{\olr}{\overline{r}}
\newcommand{\olrs}{\overline{r}^{\shp}}
\newcommand{\olrn}{\overline{r}^{\nat}}
\newcommand{\bs}{\backslash}
\newcommand{\olep}{\overline{\epsilon}}

%header material for paper
\title{Responses to referees for ``Asymmetric relationships and their effects on coexistence''}
\date{September 2023}

\begin{document}

\noindent \emph{Dear Editors,} \\

\noindent \emph{Thank you for the decision of ``minor revisions''. We have 
fully addressed the referee and editor comments below and in the manuscript.
We hope the paper can now be rapidly formally accepted. } \\

\noindent \emph{We have replied to referee comments below in italic, with each response preceded
by ``***'', to make our responses easier to find.} \\

\noindent \emph{We submit the following pdf files: The main text pdf, including all figures for readability; 
the Supporting Information; a version of the main text with changes tracked; and all figures as 
separate pdfs, for the production process. The document showing 
the changes we made does not include links such as citations and
references to figures, but it does accurately represent the changes made to the text.
We also submit...
%***DAN: all the latex files and so on.
%*%***DAN: make sure the stuff about putting a latex version of the MT at the end of the SM is all ready to go 
%*%in what I submit.
} \\

\noindent \emph{We again thank the referees and editors for their feedback and positive reviews!} \\

\noindent \emph{Yours,}

\noindent \emph{Dan Reuman and Jasmin Albert} \\


\noindent \textbf{Comments of referee 1:} \\

\noindent C1) Thank-you to the authors for their response to my comments.\\

\noindent ***\emph{We appreciate your feedback which helped to improve our manuscript; thank you.} \\

\noindent C2) I have two minor suggestions remaining which I think should be straightforward to implement.

First, to consider introducing a discussion of the robustness to more esoteric definitions of the partial-sharp distributions, and adding this briefly to the main text.  Primarily as the authors already suggest in their response letter, as a signpost for future work.\\

\noindent ***\emph{We added the requested material to section 2.3.} \\

\noindent C3) The only other minor suggestion is that the authors clarify that in Fig 1 they are simply showing that ATAs do occur in nature.  I was not suggesting that the authors include examples pertinent to their question in Figure 1---as they say, readers may not be expecting this. I don't think that the connection between the ATAs in Fig 1 and the rest of the project are that clear, as I already expressed. But I respect the authors wishes (and their other feedback) that it is worthwhile including these. Just a sentence or so at some point explaining that these are not directly related to the ATAs relevant in the remainder of the paper may avoid confusion. \\

\noindent ***\emph{We added a sentence, as requested, in the first paragraph of the Introduction.} \\

\noindent \textbf{Comments of referee 2:} \\

\noindent C4) This is a novel contribution highlighting that asymmetric tail associations in correlations between two variables was a very simple aspect not properly considered before but with huge implications for the maintenance of biodiversity. I congratulate the authors for their work. \\

\noindent ***\emph{Thank you for the very positive feedback and previous comments which helped to improve our manuscript!} \\

\noindent \textbf{Comments of referee 3:} \\

\noindent C5) I thank the authors for the change and the nice discussion/replies to my questions. I especially like the new figure 2 which greatly helped my understanding of how to remove ATA. \\
  
\noindent ***\emph{Many thanks for the positive feedback which improved our manuscript to become more understandle to other readers as well!} \\

\noindent \textbf{Comments of the editor:} \\

\noindent C6) Reviewers are enthusiastic about this paper demonstrating the importance of how variable relationships depending on when they are weak or strong influence competitive exclusion and coexistence. \\

\noindent ***\emph{Thank you for pointing out reviewers' positive feedback.} \\

\noindent C7) The legends of figures are rather long and dense. Figures should be self-explanatory. I suggest adding to all of them the sentence at the end: “See Table 1 for used annotations and abbreviations.” \\

\noindent ***\emph{We did as requested.} \\

\noindent C8) The legend in Fig. 1 is too long and has variables not present in the graphs but mentioned in other sections of the paper. For example, in line 44-45: “The variables (B1, B2) described in the Introduction…”. I suggest revising if this information is needed at all in this Figure. \\

\noindent ***\emph{We removed the variables, as requested. The editor was right, these were not
needed. Apologies for missing this previously.} \\

\noindent C9) Main concepts should be described in the introduction in a way that could be understood for a broad audience. In this sense, I suggest adding a short non- mathematical definition for storage effects even if you go in more detail in the Theory section in lines 59-60 

Page 2, Lines 59-60 “coexistence into the contributions of various mechanisms, with names such as storage effects (Chesson1994). Storage effects refer to….. Storage effects are reviewed conceptually below and defined formally in Theory. \\  

\noindent ***\emph{We did as requested.} \\

\noindent C10)  Page 2, Line 60: Start a new paragraph with the sentence “MCT has been applied to several systems…” \\

\noindent ***\emph{This seemed, to us, to be an odd request, as the sentence which followed this one is the 
last in the paragraph, so putting a new paragraph break where the referee suggested would make a very short, two
sentence paragraph, with no clear topic sentence. Furthermore, the purpose of the paragraph this sentence
is a part of is to introduce MCT, a purpose which is definitely served by these two sentences. So, to us,
these sentences seemed to fit better where they were than in a new paragraph on their own. 
So we thought about why the referee may have made such
request and whether we might be able to address the underlying issue. It seemed to us the confusion might have come
from the fact that, whereas the paragraph starts with general MCT, it then transitions to storage effects, and 
then transitions back
to general MCT at the point of the two sentences the referee has asked us to separate. 
Whereas storage effects are part of MCT, so it makes sense to mention them in a paragraph about MCT,
the transtion to storage effects and then back to general MCT might have been confusing. So we moved the
two sentences in question to earlier in the paragraph. We think this is an improvement and should, hopefully,
address the underlying issue as well as streamlining the transition to the following paragraph.} 

\end{document}